### 2020-05-04 ncov.tex
last paragraph!!!!????

>>>>

\cite{flaxman2020estimating} recently estimated the basic reproduction number for SARS-CoV-2 outbreaks in 11 European countries to be around 3.87 (3.01--4.66), on average.
While these estimates appear to be broadly consistent with to earlier estimates from China, comparing the exponential growth rate and the underlying generation-interval distributions suggest otherwise.
They assumed a shorter mean generation interval ($\bar G = 6.5\,\textrm{days}$) but similar generation-interval dispersion ($\kappa = 0.38$);
based on these values, the exponential growth rate has to be much higher ($r = 0.27\,\textrm{days}^{-1}$) to obtain $\Ro = 3.87$ compared to the exponential growth rate observed in China ($\mu_r = 0.17\,\textrm{days}^{-1}$; 95\% CI: 0.12--0.25 $\textrm{days}^{-1}$).
We caution that naively comparing estimates of the basic reproduction number without accounting for differences in underlying assumptions can underestimate the differences in the estimates.
